---
title: "NFL Winning Percentage"
author: ""
date: "Last Updated: Feb 14, 2015"
output: 
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---


```{r include=FALSE}
# Don't delete this chunk if you are using the mosaic package
# This loads the mosaic and dplyr packages
require(mosaic)
```

```{r include=FALSE}
# Some customization.  You can alter or delete as desired (if you know what you are doing).

# This changes the default colors in lattice plots.
trellis.par.set(theme=theme.mosaic())  

# knitr settings to control how R chunks work.
require(knitr)
opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small"    # slightly smaller font for code
)
# This loads the mosaic data sets.  (Could be deleted if you are not using them.)
require(mosaicData)    
require(Stat2Data)
```

This example is embedded throughout Sections 3.1 and 3.2. See the background information in Example 3.1 on p.95.

```{r}
data(NFL2007Standings)
```

## Introduction

We'd like to model `WinPct` using the other available information. 

* Show scatterplots of `WinPct` against `PointsFor` and `WinPct` against `PointsAgainst` (Fig. 3.1).

SOLUTION:

```{r}
xyplot(WinPct ~ PointsFor, data=NFL2007Standings, type=c("p", "r"))
xyplot(WinPct ~ PointsAgainst, data=NFL2007Standings, type=c("p", "r"))
```


* Which of the two variables is a more effective predictor of winning percentage for these data?

SOLUTION:

```{r}
cor(WinPct ~ PointsFor, data=NFL2007Standings)
cor(WinPct ~ PointsAgainst, data=NFL2007Standings)
```


* Consider a regression that includes both of the predictors. Write out the fitted equation.

SOLUTION:

```{r}
m1 <- lm(WinPct ~ PointsFor + PointsAgainst, data=NFL2007Standings)
summary(m1)
```

$$\widehat{WinPct} = 0.417 + 0.002 PointsFor - 0.002 PointsAgainst$$


* Consider the Pittsburgh Steelers, who scored 393 points while allowing 260 points during the 2007 season. What is the predicted winning percentage based on the model?

SOLUTION:

```{r}
pred1 <- makeFun(m1)
pred1(PointsFor=393, PointsAgainst=260)
```




* What is the associated residual? The Steelers' record showed a winning percentage of 0.625.

SOLUTION:

```{r}
0.625 - 0.714
```


* What is the **standard error of the multiple regression model**?

SOLUTION:

* Test the significance of the `PointsAgainst` predictor in the multiple regression model.

SOLUTION:

* Produce a 95% confidence interval for the size of the average improvement in winning percentage for every extra point scored during a season.

SOLUTION:

```{r}
qt(0.975, 29)
0.001766 + 2.045*0.000187
0.001766 - 2.045*0.000187

```


* Verify the calculation of $R^2$ by using a correlation calculation.

SOLUTION:

```{r}
cor(fitted(m1), NFL2007Standings$WinPct)^2
```


* Suppose an NFL team in the upcoming season scores 400 points and allows 350 points. Compute a 95% prediction interval for this team's `WinPct`.

SOLUTION:

```{r}
pred1(PointsFor=400, PointsAgainst=350, int="prediction", level=0.95)
```

