---
title: "Perch Weights"
author: ""
date: "Last Updated: Feb 15, 2015"
output: 
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---


```{r include=FALSE}
# Don't delete this chunk if you are using the mosaic package
# This loads the mosaic and dplyr packages
require(mosaic)
```

```{r include=FALSE}
# Some customization.  You can alter or delete as desired (if you know what you are doing).

# This changes the default colors in lattice plots.
trellis.par.set(theme=theme.mosaic())  

# knitr settings to control how R chunks work.
require(knitr)
opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small"    # slightly smaller font for code
)
# This loads the mosaic data sets.  (Could be deleted if you are not using them.)
require(mosaicData)    
require(Stat2Data)
```

This example is embedded throughout Sections 3.4 to 3.6. See the background information in Example 3.10 on p.118.

```{r}
data(Perch)
```

### Introduction

We'd like to model `Weight` using the other available information. 

```{r}
head(Perch)
```

### Choose

We might imagine that weight is proportional to the area of the fish, which we can roughly approximate using `Length` times `Width`.

### Fit

* Fit a model that includes `Length`, `Width`, and `Length` times `Width` as an interaction.

SOLUTION:

### Assess

* The `Length` predictor does not appear to be significant in the model. Should we remove it?

SOLUTION:

* Look at a residual versus fitted value plot of this model and discuss what you see.

SOLUTION:

### Fit (Again)

* Now fit a complete second-order model for the weights of the perch  using the same two variables.

SOLUTION:

### Assess (Again)

* How does this new model compare to the model without quadratic terms?

SOLUTION:

### Collinearity

* Consider a smaller model with only the linear terms of `Length` and `Width`, with no interaction term. Compare the coefficients of this model to the model that has an interaction term.

SOLUTION:

### Nested F-Test

* Compare the complete second-order model to the original model with an interaction between `Length` and `Width` using an F-test. What do you conclude?

SOLUTION:


