---
title: "Election 2000: Unusual Points"
author: ""
date: "Last Updated: Feb 22, 2015"
output: 
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---


```{r include=FALSE}
# Don't delete this chunk if you are using the mosaic package
# This loads the mosaic and dplyr packages
require(mosaic)
```

```{r include=FALSE}
# Some customization.  You can alter or delete as desired (if you know what you are doing).

# This changes the default colors in lattice plots.
trellis.par.set(theme=theme.mosaic())  

# knitr settings to control how R chunks work.
require(knitr)
opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small"    # slightly smaller font for code
)
# This loads the mosaic data sets.  (Could be deleted if you are not using them.)
require(mosaicData)    
require(Stat2Data)
```

This corresponds to Example 4.3 on p. 180 and Example 4.5 on p. 184.


```{r}
data(PalmBeach)
```

## The Data

Previously in Example 1.9 on p. 49, we looked at a model using Bush votes to predict Buchanan votes in Florida counties. You'll recall we identified quite a few unusual observations.

```{r}
m1 <- lm(Buchanan ~ Bush, data=PalmBeach)
summary(m1)
xyplot(Buchanan ~ Bush, data=PalmBeach, type=c("p", "r"))
```

## Leverage

Suppose we go with the "three times typical" rule. What should the cutoff be for identifying high leverage points?

SOLUTION:

```{r}

```


Identify these observations in the dataset.

SOLUTION:

```{r}

```

## Standardized and Studentized Residuals

Identify all observations which either have high leverage or high standardized/studentized residuals based on the "three times typical" rule.

SOLUTION:

```{r}

```

## Cook's Distance

Show Cook's distance for Palm Beach County, Dade County, and Orange County.

SOLUTION:

```{r}

```



