---
title: "House Prices: Added Variable Plots"
author: ""
date: "Last Updated: Feb 22, 2015"
output: 
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---


```{r include=FALSE}
# Don't delete this chunk if you are using the mosaic package
# This loads the mosaic and dplyr packages
require(mosaic)
```

```{r include=FALSE}
# Some customization.  You can alter or delete as desired (if you know what you are doing).

# This changes the default colors in lattice plots.
trellis.par.set(theme=theme.mosaic())  

# knitr settings to control how R chunks work.
require(knitr)
opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small"    # slightly smaller font for code
)
# This loads the mosaic data sets.  (Could be deleted if you are not using them.)
require(mosaicData)    
require(Stat2Data)
```

This corresponds to Example 4.1 on p. 165 in the textbook.


```{r}
data(Houses)
```

## The Data

In Example 3.14, house `Price` was modeled using the two correlated predictors `Size` and `Lot` ($r=0.767$). A natural question to ask is, exactly what contribution does `Size` provide after accounting for `Lot`?

## Added Variable Plots (Manual Method)

1. Find the residuals when predicting `Price` without `Size`.

SOLUTION: 

```{r}
m1 <- lm(Price ~ Lot, data=Houses)
resid(m1)
```

2. Find the residuals when predicting `Size` using the other predictor `Lot`.

SOLUTION:

```{r}
m2 <- lm(Size ~ Lot, data=Houses)
resid(m2)
```

3. Plot the residuals from the first model against the residuals from the second model for the **added variable plot**.

SOLUTION:

```{r}
xyplot(resid(m1) ~ resid(m2), type=c("p", "r"))
```

## Added Variable Plots (Using `avPlot()`)

Using the `avPlot()` function in the `car` package (bundled into the `mosaic` package), we can reproduce the plot without going through the 3-step process. Give it a shot:

SOLUTION:

```{r}
m3 <- lm(Price ~ Lot + Size, data=Houses)
avPlot(m3, "Size")
```

## Interpretation

What does the added variable plot tell us?

SOLUTION:

```{r}
cor(resid(m1), resid(m2))
```

