---
title: "Another Look at Fruitflies"
author: ""
date: "Last Updated: July 30, 2015"
output: 
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---
```{r include=FALSE}
# Don't delete this chunk if you are using the mosaic package
# This loads the mosaic and dplyr packages
require(mosaic)
```

```{r include=FALSE}
# Some customization.  You can alter or delete as desired (if you know what you are doing).

# This changes the default colors in lattice plots.
trellis.par.set(theme=theme.mosaic())  

# knitr settings to control how R chunks work.
require(knitr)
opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small"    # slightly smaller font for code
)
# This loads the mosaic data sets.  (Could be deleted if you are not using them.)
require(mosaicData)                
require(Stat2Data)
```

This corresponds to a series of examples in Chapter 7, starting with Example 7.4 on p. 332. 

## The Data

In Chapter 5, we used the `FruitFlies` dataset to examine whether or not the mean lifespan of male fruit flies depended on the kind of mate(s) it resided with. 

```{r}
data(FruitFlies)
head(FruitFlies)
```

Earlier, we found that mean lifespans of male fruit flies differed depending on the number/type of females it resided with.

```{r}
m1 <- lm(Longevity ~ Treatment, data=FruitFlies)
anova(m1)
```

## Multiple Comparisons

* Review: Run Fisher's LSD to see which pairs of treatments are determined to have significantly different means at an alpha level of 0.05.

SOLUTION:

```{r}
with(FruitFlies, pairwise.t.test(Longevity, Treatment, p.adjust.method = "none"))
```

* Use the Bonferroni correction to see which pairs of treatments are determined to have significantly different means at an alpha level of 0.05. What do you conclude?

SOLUTION:

```{r}
with(FruitFlies, pairwise.t.test(Longevity, Treatment, p.adjust.method = "bonf"))

```

* What is the relationship between the p-values in the two tables above?

SOLUTION:

* Use Tukey's HSD to see which pairs of treatments are determined to have significantly different means at an alpha level of 0.05. What do you conclude?

SOLUTION:

```{r}
TukeyHSD(m1)
```

## 2 Sample Comparisons

Now, we will consider a subset of the dataset which contains 25 fruit flies in the 8 virgins group and the 25 fruit flies living alone and consider the similarities betwen regression and a two-sample comparison of means. 

* Use the `filter()` function to create a new dataset, called `FruitFlies1` which only contains the 2 groups of interest.

SOLUTION:

```{r}
FruitFlies1 <- filter(FruitFlies, Treatment %in% c("8 virgin", "none"))

```


* Compute the sample mean of each group.

SOLUTION:

```{r}
mean(Longevity ~ Treatment, data=FruitFlies1)
```

* Produce a dot plot (using `dotPlot()`) like Figure 7.8 to illustrate the difference in lifespans of the two different groups. 

SOLUTION:

```{r}
dotPlot(~ Longevity | Treatment, layout=c(1, 2), data=FruitFlies1, nint=15, cex=0.3)
```

* Perform a **pooled** two-sample t-test on the data. What do you conclude?

SOLUTION:

```{r}
t.test(Longevity ~ Treatment, data=FruitFlies1, var.equal=TRUE)
```

* Perform an ANOVA to address the same question. What do you discover? 

SOLUTION:

```{r}
m2 <- lm(Longevity ~ Treatment, data=FruitFlies1)
anova(m2)
```

* Fit a regression model using `Treatment = "none"` as the reference level. Show the regression summary.

SOLUTION:

```{r}
FruitFlies1 <- mutate(FruitFlies1, Treatment = relevel(Treatment, "none"))
m2 <- lm(Longevity ~ Treatment, data=FruitFlies1)

summary(m2)
```

* Compare the results of the linear regression (and its associated ANOVA table) to the results of the pooled 2-sample t-test.

SOLUTION:



## Back to the Entire Sample

* Fit a regression model using `Treatment = "none"` as the reference level. Show the regression summary.

SOLUTION:

```{r}
FruitFlies <- mutate(FruitFlies, Treatment = relevel(Treatment, "none"))
m3 <- lm(Longevity ~ Treatment, data=FruitFlies)

summary(m3)
```

* What do you learn from the p-values in the linear model summary above? What do you learn from the p-value in the ANOVA table?

SOLUTION:

```{r}
anova(m3)
```

