---
title: "Ants on Sandwiches"
author: ""
date: "Last Updated: July 29, 2015"
output: 
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---
```{r include=FALSE}
# Don't delete this chunk if you are using the mosaic package
# This loads the mosaic and dplyr packages
require(mosaic)
```

```{r include=FALSE}
# Some customization.  You can alter or delete as desired (if you know what you are doing).

# This changes the default colors in lattice plots.
trellis.par.set(theme=theme.mosaic())  

# knitr settings to control how R chunks work.
require(knitr)
opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small"    # slightly smaller font for code
)
# This loads the mosaic data sets.  (Could be deleted if you are not using them.)
require(mosaicData)                
require(Stat2Data)
```

This is taken from Example 7.16 in the book on p.364.

## The Data

```{r}
data(SandwichAnts)
summary(SandwichAnts)
```

We would like to use this dataset to explore the similarities between linear regression (with indicators) and two-way ANOVA. 

* Calculate the mean numbers of ants on sandwiches as presented in Table 7.2.

SOLUTION:

```{r}

```

## Analysis

* Perform a two way ANOVA with interaction effects using the two variables, `Filling` and `Bread`. What do you conclude?

SOLUTION:

```{r}

```

* Compare what you learn from the ANOVA table to what you learn from the linear regression summary.

SOLUTION:

```{r}

```
