---
title: "Walking Babies (A Study in Contrasts)"
author: ""
date: "Last Updated: July 30, 2015"
output: 
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---
```{r include=FALSE}
# Don't delete this chunk if you are using the mosaic package
# This loads the mosaic and dplyr packages
require(mosaic)
```

```{r include=FALSE}
# Some customization.  You can alter or delete as desired (if you know what you are doing).

# This changes the default colors in lattice plots.
trellis.par.set(theme=theme.mosaic())  

# knitr settings to control how R chunks work.
require(knitr)
opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small"    # slightly smaller font for code
)
# This loads the mosaic data sets.  (Could be deleted if you are not using them.)
require(mosaicData)                
require(Stat2Data)
```

This corresponds to Example 7.10 on p. 341.

## The Data

```{r}
data("WalkingBabies")
summary(WalkingBabies)
```

An experiment was done to see if it would be possible to get babies to learn walking sooner with a set of special exercises. 4 treatment groups were used, detailed on p.342.

* Given the descriptions of the treatment groups, reorder the levels of the `Group` variable in a sensible manner.

SOLUTION:

```{r}

```

## Visualize

* Show a plot comparing age at walking (in months) to treatment group. Describe what you see.

SOLUTION:

```{r}

```

* Your textbook describes that there are essentially 3 control groups. Why?

SOLUTION:

## Fit

* Run a one-way ANOVA on the data. Describe what you learn.

SOLUTION:

```{r}

```

## Tests

Is there a difference between the group that received the special exercises and the group that were just told to exercise?

* Run a suitable test to answer this question.

SOLUTION:

```{r}

```


* Does using any exercises give a different mean time to walking relative to no exercises?

SOLUTION:

```{r}

```

* The textbook says that further inspection of the differences between (combinations of) groups is justified despite a fail to reject at the F-test level. Explain why this discussion is relevant, i.e. why should we be wary of just blindly applying many such tests.

SOLUTION: