---
title: "Cancer Survivability"
author: ""
date: "Last Updated: July 21, 2015"
output: 
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r include=FALSE}
# Don't delete this chunk if you are using the mosaic package
# This loads the mosaic and dplyr packages
require(mosaic)
```

```{r include=FALSE}
# Some customization.  You can alter or delete as desired (if you know what you are doing).

# This changes the default colors in lattice plots.
trellis.par.set(theme=theme.mosaic())  

# knitr settings to control how R chunks work.
require(knitr)
opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small"    # slightly smaller font for code
)
# This loads the mosaic data sets.  (Could be deleted if you are not using them.)
require(mosaicData)                
require(Stat2Data)
```

This corresponds to Example 5.8 starting on p.243.

### The Data

```{r}
data(CancerSurvival)
head(CancerSurvival)
```

We'd like to consider whether the effect of ascorbate differs between which organs were affected by cancer. What model should we use?

### Fit 

* Provide a table of summary statistics for survival time broken down by each type of organ. Also, compute the group effects.

SOLUTION:

```{r}
favstats(Survival ~ Organ, data = CancerSurvival)
mean(~Survival, data = CancerSurvival)
mean(Survival ~ Organ, data = CancerSurvival) - 
     mean(~ Survival, data = CancerSurvival)
```

* Fit the ANOVA model.

SOLUTION:

```{r}
m1 <- lm(Survival ~ Organ, data=CancerSurvival)
anova(m1)
```

### Assess & Use

* Check the assumption constant variance condition both numerically and graphically.

SOLUTION:

```{r}
sds <- sd(Survival ~ Organ, data=CancerSurvival)
max(sds)/min(sds)

xyplot(resid(m1) ~ fitted(m1), data=CancerSurvival)
```

* Check the normality assumption via a normal quantile plot.

```{r, fig.keep = 'last'}
qqmath(~resid(m1))
ladd(panel.qqmathline(resid(m1)))
```

* Does the model satisfy the necessary conditions for the ANOVA model? If not, consider possible transformations to resolve these issues and re-assess the new model.

SOLUTION: 

```{r}
m2 <- lm(log(Survival)~Organ, data=CancerSurvival)
favstats(log(Survival) ~ Organ, data=CancerSurvival)
mean(log(Survival) ~ Organ, data=CancerSurvival) - 
  mean(log(Survival), data=CancerSurvival)

sds <- sd(log(Survival)~Organ,data=CancerSurvival)
max(sds)/min(sds)

xyplot(resid(m2)~fitted(m2),data=CancerSurvival)
```

```{r, fig.keep='last'}
qqmath(~resid(m2))
ladd(panel.qqmathline(resid(m2)))
```


* Report the ANOVA table. What conclusions can we make?

SOLUTION:

```{r}
anova(m2)
```

