---
title: "Diamonds"
author: ""
date: "Last Updated: July 21, 2015"
output: 
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r include=FALSE}
# Don't delete this chunk if you are using the mosaic package
# This loads the mosaic and dplyr packages
require(mosaic)
```

```{r include=FALSE}
# Some customization.  You can alter or delete as desired (if you know what you are doing).

# This changes the default colors in lattice plots.
trellis.par.set(theme=theme.mosaic())  

# knitr settings to control how R chunks work.
require(knitr)
opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small"    # slightly smaller font for code
)
# This loads the mosaic data sets.  (Could be deleted if you are not using them.)
require(mosaicData)    
require(Stat2Data)
```

This corresponds to Example 5.7 on p.238.

```{r}
data(Diamonds2)
```

### The Data

We've all heard of the 4 C's for diamonds -- cut, color, clarity, and carat. These four jointly determine the price of a diamond and our dataset contains 307 diamonds with these variables recorded.

```{r}
summary(Diamonds2)
```

### Fit

A buyer may be interested in knowing if a particular color of diamond is associated with more or fewer carats. 

* Replicate the information in the table on the bottom of p. 238. 

SOLUTION:

```{r}
favstats(Carat~Color,data=Diamonds2)  
favstats(~Carat,data=Diamonds2)
```


* Compute the treatment effects. 

SOLUTION:

```{r}
mean(Carat~Color,data=Diamonds2) - mean(~Carat, data=Diamonds2)
```

### Assess

* Check the conditions for the model. Produce a plot that illustrates the amount of variability between groups. (Figure 5.5)

SOLUTION:

```{r}
m1 <- lm(Carat~Color,data=Diamonds2)
xyplot(resid(m1)~fitted(m1), type=c("p", "r"))
```

* Produce a normal quantile plot of residuals (similar to Figure 5.6(a)).

SOLUTION:

```{r, fig.keep = 'last'}
qqmath(~resid(m1))
ladd(panel.qqmathline(resid(m1)))
```

* Produce side-by-side histograms (similar to Figure 5.6(b)) showing the distribution of carat within each category of color.

```{r}
histogram(~ Carat | Color,data=Diamonds2)
```

* Does the model satisfy the assumptions? If not, what is one possible transformation? 

SOLUTION: 

* Recheck the model assumptions on the transformed data.

SOLUTION:

```{r}
m2 <- lm(log(Carat) ~ Color, data=Diamonds2)
xyplot(resid(m2) ~ fitted(m2))
```

```{r, fig.keep = 'last'}
qqmath(~resid(m2))
ladd(panel.qqmathline(resid(m2)))
```



* Is there a difference among the means of the (possibly transformed) number of carats based on the color of the diamonds?

SOLUTION:

```{r}
anova(m2)
```
