---
title: "Fruitflies (Part 2)"
author: ""
date: "Last Updated: July 21, 2015"
output: 
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---
```{r include=FALSE}
# Don't delete this chunk if you are using the mosaic package
# This loads the mosaic and dplyr packages
require(mosaic)
```

```{r include=FALSE}
# Some customization.  You can alter or delete as desired (if you know what you are doing).

# This changes the default colors in lattice plots.
trellis.par.set(theme=theme.mosaic())  

# knitr settings to control how R chunks work.
require(knitr)
opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small"    # slightly smaller font for code
)
# This loads the mosaic data sets.  (Could be deleted if you are not using them.)
require(mosaicData)    
require(Stat2Data)
```

This corresponds to the last Fruitfly example, Example 5.11 on p. 255.


## The Data

In this chapter, we explore how reproductive behavior affects longevity in fruit flies. The data are loaded below:

```{r}
data(FruitFlies)
```



### Example 5.11

Having rejected the null hypothesis, we conclude that there is at least one group that has a group mean significantly different from the others. We'd want to figure out which, specifically, the differing group(s) is/are. 


* Use Fisher's LSD to do all the pairwise comparisons. What do you conclude at the alpha = 0.05 level?

SOLUTION:

```{r}
with(FruitFlies, pairwise.t.test(Longevity, Treatment, p.adj="none"))
```