---
title: "Hawks"
author: ""
date: "Last Updated: July 21, 2015"
output: 
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---
```{r include=FALSE}
# Don't delete this chunk if you are using the mosaic package
# This loads the mosaic and dplyr packages
require(mosaic)
```

```{r include=FALSE}
# Some customization.  You can alter or delete as desired (if you know what you are doing).

# This changes the default colors in lattice plots.
trellis.par.set(theme=theme.mosaic())  

# knitr settings to control how R chunks work.
require(knitr)
opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small"    # slightly smaller font for code
)
# This loads the mosaic data sets.  (Could be deleted if you are not using them.)
require(mosaicData)    
require(Stat2Data)
```

This corresponds to Example 5.9 on p. 247.

### The Data 

Data are collected by researchers at Cornell on random samples of three different species of hawks: red-tailed,sharp-shinned, and Cooper's hawks. We are interested in the tail lengths of these birds and how they might vary between different species.  

```{r}
data(Hawks)
head(Hawks)
```

### Fit

* Calculate group means and the grand mean. Then calculate the treatment effects for the one-way ANOVA model.

SOLUTION:

```{r}
favstats(Tail ~ Species, data=Hawks)
mean(~Tail, data=Hawks)

mean(Tail ~ Species, data=Hawks) - mean(~Tail, data=Hawks)
```

* Fit the model.

SOLUTION:

```{r}
m1 <- lm(Tail~Species,data=Hawks)
```


### Assess

* Check the conditions for the model.

SOLUTION:

```{r, fig.keep='last'}
xyplot(resid(m1)~fitted(m1))
```

```{r, fig.keep='last'}
qqmath(~resid(m1))
ladd(panel.qqmathline(resid(m1)))
```

* What can we conclude?

SOLUTION: