---
title: "Author with a club"
author: ""
date: "Last Updated: August 5, 2015"
output: 
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---
```{r include=FALSE}
# Don't delete this chunk if you are using the mosaic package
# This loads the mosaic and dplyr packages
require(mosaic)
```

```{r include=FALSE}
# Some customization.  You can alter or delete as desired (if you know what you are doing).

# This changes the default colors in lattice plots.
trellis.par.set(theme=theme.mosaic())  

# knitr settings to control how R chunks work.
require(knitr)
opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small"    # slightly smaller font for code
)
# This loads the mosaic data sets.  (Could be deleted if you are not using them.)
require(mosaicData)                
require(Stat2Data)
```

This is adapted from Examples 9.10 (p. 469) and 9.16 (p. 485) of the book. 

## The Data

In this example, we consider the rate of success on the golf course as a function of the length of the putt. 

```{r}
data(Putts1)
summary(Putts1)
```

## Choose and Fit

We'd like to begin by constructing an empirical logit plot to assess whether a logistic regression model would be appropriate.

* Replicate the empirical logits in Table 9.5 in preparation for making the plot.

SOLUTION:

```{r}

```

* Make the empirical logit plot based on these numbers.

SOLUTION:

```{r}

```

* Replicate the table on the bottom of p. 469. What does this table aim to achieve?

SOLUTION:

```{r}


```


## Assess and Use

* Display and interpret the model summary for your logistic regression model.

SOLUTION:

```{r}


```

* Calculate the likelihood test statistic based on the summary table. Compare it to a chi-square distribution with appropriate degree of freedom. What do you conclude?

SOLUTION: 

```{r}

```


* Confirm that the `anova()` calculation matches what you found above.

SOLUTION: 

```{r}

```

