---
title: "Pig Feed"
author: ""
date: "Last Updated: July 28, 2015"
output: 
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r include=FALSE}
# Don't delete this chunk if you are using the mosaic package
# This loads the mosaic and dplyr packages
require(mosaic)
```

```{r include=FALSE}
# Some customization.  You can alter or delete as desired (if you know what you are doing).

# This changes the default colors in lattice plots.
trellis.par.set(theme=theme.mosaic())  

# knitr settings to control how R chunks work.
require(knitr)
opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small"    # slightly smaller font for code
)
# This loads the mosaic data sets.  (Could be deleted if you are not using them.)
require(mosaicData)                
require(Stat2Data)
```

This is taken from Example 6.4 on p.287. 

## The Data

What factor(s) play in a role in weight gain for pigs? Here we consider the roles of antibiotics and vitamin B12.

```{r}
data(PigFeed)
summary(PigFeed)
```

Let's start by examining the average weight gain for each diet, which is identified by whether or not antibiotics (Factor A) and/or vitamin B12 (Factor B) is/are present.

* Show the table of averages across each combination of the two factors, as in the right side-table in Table 6.7.

SOLUTION:

```{r}

```

* Compute the differences in mean weight gain due to B12 (values in second table on p. 288).

SOLUTION:

```{r}

```

* Compute the differences in mean weight gain due to antibiotics (values in third table on p. 288).

SOLUTION:

```{r}

```

* Produce two possible interaction plots for these data. Which one is easier to read?

SOLUTION:

```{r}

```

* Challenge: What's happening in Figure 6.7? How did the data points come about? Generate the numbers that would be used in these two plots.

SOLUTION: 

```{r}

```

* Which of the two models appears more appropriate? Two-way additive or two-way with interaction?

SOLUTION:

```{r}

```

