---
title: "Butterfly Ballot (Choose)"
author: ""
date: "Last Updated: Feb 5, 2015"
output: 
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---


```{r include=FALSE}
# Don't delete this chunk if you are using the mosaic package
# This loads the mosaic and dplyr packages
require(mosaic)
```

```{r include=FALSE}
# Some customization.  You can alter or delete as desired (if you know what you are doing).

# This changes the default colors in lattice plots.
trellis.par.set(theme=theme.mosaic())  

# knitr settings to control how R chunks work.
require(knitr)
opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small"    # slightly smaller font for code
)
# This loads the mosaic data sets.  (Could be deleted if you are not using them.)
require(mosaicData)    
require(Stat2Data)
```

This exercise corresponds to Example 1.9 beginning on p.49 of the text.

```{r}
data(PalmBeach)
```

## Introduction

In this example, we revisit Election 2000, where Palm Beach County (where Prof. Wang was living at the time!) used a nonstandard ballot. Critics claimed that people accidentally voted for Buchanan when they intended to vote for someone else. To investigate this problem, we'll look at a model predicting the number of votes for Buchanan using the number of votes for Bush across all Florida counties. 

## Scatterplot

Plot the relationship between `Buchanan` and `Bush` (Figure 1.23). Highlight Palm Beach County using a different color.

SOLUTION:

```{r}
xyplot(Buchanan ~ Bush, data=PalmBeach)
head(PalmBeach)
xyplot(Buchanan ~ Bush, data=PalmBeach, col=1+(PalmBeach$County == "PALM BEACH"))
 
```


