---
title: "Butterfly Ballot (Fit)"
author: ""
date: "Last Updated: Feb 5, 2015"
output: 
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---


```{r include=FALSE}
# Don't delete this chunk if you are using the mosaic package
# This loads the mosaic and dplyr packages
require(mosaic)
```

```{r include=FALSE}
# Some customization.  You can alter or delete as desired (if you know what you are doing).

# This changes the default colors in lattice plots.
trellis.par.set(theme=theme.mosaic())  

# knitr settings to control how R chunks work.
require(knitr)
opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small"    # slightly smaller font for code
)
# This loads the mosaic data sets.  (Could be deleted if you are not using them.)
require(mosaicData)    
require(Stat2Data)
```

This exercise corresponds to Example 1.9 beginning on p.49 of the text.

```{r}
data(PalmBeach)
```

## Recap

Although there are a few outliers in the scatterplot of `Bush` against `Buchanan`, a simple linear regression still appears to be appropriate. 

## Fit the Model

Fit the linear model using all data points. Display the model summary.

SOLUTION:

```{r}
m1 <- lm(Buchanan ~ Bush, data=PalmBeach)
summary(m1)
```

$$ \widehat{Buchanan} = 45.29 + 4.917\times 10^{-3} Bush$$

Fit the linear model excluding Palm Beach County. Display the model summary.

SOLUTION:

```{r}
PalmBeach2 <- filter(PalmBeach, County != "PALM BEACH")
m2 <- lm(Buchanan ~ Bush, data=PalmBeach2)
summary(m2)
```

$$ \widehat{Buchanan} = 65.57 + 3.482\times 10^{-3} Bush$$

Display both regression lines on a scatterplot with all counties. 

SOLUTION:

```{r}
xyplot(Buchanan ~ Bush, data=PalmBeach, type=c("p", "r"))
ladd(panel.abline(m2, col="red"))
```

