---
title: "Doctors and Hospitals II (Choose)"
author: ""
date: "Last Updated: Jan 27, 2015"
output: 
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---


```{r include=FALSE}
# Don't delete this chunk if you are using the mosaic package
# This loads the mosaic and dplyr packages
require(mosaic)
```

```{r include=FALSE}
# Some customization.  You can alter or delete as desired (if you know what you are doing).

# This changes the default colors in lattice plots.
trellis.par.set(theme=theme.mosaic())  

# knitr settings to control how R chunks work.
require(knitr)
opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small"    # slightly smaller font for code
)
# This loads the mosaic data sets.  (Could be deleted if you are not using them.)
require(mosaicData)    
require(Stat2Data)
```

This exercise corresponds to the second part of Example 1.6 beginning on p.42 of the text.

```{r}
data(MetroHealth83)
```

## Recap

We have determined that a straight up linear regression model on the untransformed variables `NumHospitals` and `NumMDs` is not appropriate. In this part of the exercise, we'll explore using a **square root transformation**.

## Check with a Plot

Produce a scatterplot of the square root of `NumMDs` against the `NumHospitals`. This should look like Figure 1.14 on p. 42. 

Hint: The `sqrt()` function can be used to calculate the square root.

SOLUTION:

```{r}

```

