---
title: "Doctors and Hospitals I (Fit)"
author: ""
date: "Last Updated: Jan 27, 2015"
output: 
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---


```{r include=FALSE}
# Don't delete this chunk if you are using the mosaic package
# This loads the mosaic and dplyr packages
require(mosaic)
```

```{r include=FALSE}
# Some customization.  You can alter or delete as desired (if you know what you are doing).

# This changes the default colors in lattice plots.
trellis.par.set(theme=theme.mosaic())  

# knitr settings to control how R chunks work.
require(knitr)
opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small"    # slightly smaller font for code
)
# This loads the mosaic data sets.  (Could be deleted if you are not using them.)
require(mosaicData)    
require(Stat2Data)
```

This exercise corresponds to Example 1.6 on p.39 of the text.

```{r}
data(MetroHealth83)
```

## Recap

In the Choose step, we've discovered a positive association between `NumMDs` and `NumHospitals`, although the association may not be linear. We'll proceed to fit a linear model anyway to see how unmet assumptions are manifested in the diagnostic plots (in the Assess step).


## Fit the Model

Go ahead and fit the model using the `lm()` function and look at the model parameter estimates using `summary()`.

SOLUTION:

```{r}
m1 <- lm(NumMDs ~ NumHospitals, data=MetroHealth83)
summary(m1)
```

