---
title: "Doctors and Hospitals I (Choose)"
author: ""
date: "Last Updated: Jan 27, 2015"
output: 
  html_document:
    fig_height: 3
    fig_width: 5 
  word_document:
    fig_height: 3
    fig_width: 5
---


```{r include=FALSE}
# Don't delete this chunk if you are using the mosaic package
# This loads the mosaic and dplyr packages
require(mosaic)
```

```{r include=FALSE}
# Some customization.  You can alter or delete as desired (if you know what you are doing).

# This changes the default colors in lattice plots.
trellis.par.set(theme=theme.mosaic())  

# knitr settings to control how R chunks work.
require(knitr)
opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small"    # slightly smaller font for code
)
# This loads the mosaic data sets.  (Could be deleted if you are not using them.)
require(mosaicData)    
require(Stat2Data)
```

This exercise corresponds to Example 1.6 on p.39 of the text.

## Introduction

This dataset is stored in the variable called `MetroHealth83`. We'll start by loading this into the environment:

```{r}
data(MetroHealth83)
head(MetroHealth83)
tail(MetroHealth83)
```

There are a lot of variables, but we're interested in only 2 of them. Our goal is to try to predict the number of MDs `NumMDs` from the number of hospitals `NumHospitals`.


## Scatterplot

As a first step to choosing an appropriate model, produce a scatterplot of the variables of interest:

SOLUTION:

```{r}
xyplot(NumMDs ~ NumHospitals, data=MetroHealth83)
```

Describe the relationship seen in the scatterplot above.

SOLUTION:



Should we fit a linear model? 

SOLUTION:

