---
title: "Doctors and Hospitals I (Assess)"
author: ""
date: "Last Updated: Jan 27, 2015"
output: 
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---


```{r include=FALSE}
# Don't delete this chunk if you are using the mosaic package
# This loads the mosaic and dplyr packages
require(mosaic)
```

```{r include=FALSE}
# Some customization.  You can alter or delete as desired (if you know what you are doing).

# This changes the default colors in lattice plots.
trellis.par.set(theme=theme.mosaic())  

# knitr settings to control how R chunks work.
require(knitr)
opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small"    # slightly smaller font for code
)
# This loads the mosaic data sets.  (Could be deleted if you are not using them.)
require(mosaicData)    
require(Stat2Data)
```

This exercise corresponds to Example 1.6 on p.39 of the text.

```{r}
data(MetroHealth83)
```

## Recap

In the Fit step, we found the following model.

```{r}
m1 <- lm(NumMDs ~ NumHospitals, data=MetroHealth83)
summary(m1)
```

This can be expressed in the following equation:

$$ \widehat{NumMDs} = -385.10 + 282.01 NumHospitals $$  

Let's now see if the conditions are met.

## A First Glance

Produce a scatterplot of `NumMDs` by `NumHospitals` with the regression line superimposed. This should look like Figure 1.12(a) on p. 41.

SOLUTION:

```{r}

```

## Residuals versus Fitted Values

Produce a scatterplot of residuals against the fitted values. This should look like Figure 1.12(b) on p. 41.

SOLUTION:

```{r}

```

Describe what the two plots above tell you about the assumptions.

SOLUTION:

## Normality

Now replicate the histogram of the residuals (Figure 1.13(a)) and the normal quantile plot of the residuals (Figure 1.13(b)).

SOLUTION:

```{r}

```

Discuss what these two plots tell you about the normality assumption.

SOLUTION:


Is the linear model fitted appropriate for the data?

SOLUTION:


