---
title: "Porsche Prices (Choose)"
author: ""
date: "Last Updated: Jan 24, 2015"
output: 
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---


```{r include=FALSE}
# Don't delete this chunk if you are using the mosaic package
# This loads the mosaic and dplyr packages
require(mosaic)
```

```{r include=FALSE}
# Some customization.  You can alter or delete as desired (if you know what you are doing).

# This changes the default colors in lattice plots.
trellis.par.set(theme=theme.mosaic())  

# knitr settings to control how R chunks work.
require(knitr)
opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small"    # slightly smaller font for code
)
# This loads the mosaic data sets.  (Could be deleted if you are not using them.)
require(mosaicData)    
require(Stat2Data)
```

This exercise corresponds to Example 1.2 on p.27 of the text.

## Introduction

The dataset description and research question are provided in Example 1.1 on p.25 of the text. Quoted from the text:

> We are interested in predicting the price of a used Porsche based on its mileage, so the explanatory variable is _Mileage_ and the response is _Price_, and both variables are quantitative.

This dataset is stored in the variable called `PorschePrice`. We'll start by loading this into the environment:

```{r}
data(PorschePrice)
```

We can peek at the dataset below:
```{r}
head(PorschePrice)
```

Note that both `Price` and `Mileage` are in thousands.

## Scatterplot

As a first step to choosing an appropriate model, produce a scatterplot of the variables of interest:

SOLUTION:

```{r}

```

Describe the relationship seen in the scatterplot above.

SOLUTION:



What is the form of the model we would like to fit?

SOLUTION:

