---
title: "Porsche Prices (Fit)"
author: ""
date: "Last Updated: Jan 24, 2015"
output: 
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---


```{r include=FALSE}
# Don't delete this chunk if you are using the mosaic package
# This loads the mosaic and dplyr packages
require(mosaic)
```

```{r include=FALSE}
# Some customization.  You can alter or delete as desired (if you know what you are doing).

# This changes the default colors in lattice plots.
trellis.par.set(theme=theme.mosaic())  

# knitr settings to control how R chunks work.
require(knitr)
opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small"    # slightly smaller font for code
)
# This loads the mosaic data sets.  (Could be deleted if you are not using them.)
require(mosaicData)    
require(Stat2Data)
```

This exercise corresponds to Example 1.3 on p.29 and Example 1.4 on p.32 of the text.

```{r}
data(PorschePrice)
```

## Objective
Recall that we would like to fit the following model to the dataset `PorschePrice`:

$$Price = \beta_0 + \beta_1 Mileage + \epsilon$$

## Fitting the Model
Use the `lm()` function to fit this model and the `summary()` function to view the model summary.

SOLUTION:
```{r}

```

Interpret the coefficients. (Be careful with units!)

SOLUTION:


## Make a Prediction
Car 1 had a mileage level of 21.5 and a price of 69.4 (thousand dollars). Calculate the residual for this car from the model.

SOLUTION:

```{r}

```

## Residual Standard Error

What is the **sum of squared residuals** (SSE) from the model? 

SOLUTION:

```{r}

```

What is the residual standard error from the model? Confirm the calculation using the formula containing SSE:

SOLUTION:

```{r}

```

Interpret the residual standard error in the context of the problem.

SOLUTION:

