---
title: "Porsche Prices (Use)"
author: ""
date: "Last Updated: Jan 24, 2015"
output: 
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---


```{r include=FALSE}
# Don't delete this chunk if you are using the mosaic package
# This loads the mosaic and dplyr packages
require(mosaic)
```

```{r include=FALSE}
# Some customization.  You can alter or delete as desired (if you know what you are doing).

# This changes the default colors in lattice plots.
trellis.par.set(theme=theme.mosaic())  

# knitr settings to control how R chunks work.
require(knitr)
opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small"    # slightly smaller font for code
)
# This loads the mosaic data sets.  (Could be deleted if you are not using them.)
require(mosaicData)    
require(Stat2Data)
```

This exercise corresponds to the second part of Example 1.5 on p.38 of the text.

```{r}
data(PorschePrice)
```

## Objective
We would like to apply the model previously fit to the dataset `PorschePrice`:

```{r}
lm0 <- lm(Price ~ Mileage, data=PorschePrice)
summary(lm0)
```


## Prediction
From the text:
> For example, suppose we find a used Porsche for sale with 50,000 miles and we believe that it is from the same population from which our sample of 30 used Porsches was drawn. What should we expect to pay for this car? 

Make a prediction for the price of this car using the model.

SOLUTION:

```{r}
porsche <- makeFun(lm0)
porsche(Mileage=50)
```

Again, from the text:
> Would it be an especially good deal if the owner was asking \$38,000?

What do you think?

SOLUTION: 

```{r}

```


