---
title: "Porsche Prices (Assess)"
author: ""
date: "Last Updated: Jan 24, 2015"
output: 
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---


```{r include=FALSE}
# Don't delete this chunk if you are using the mosaic package
# This loads the mosaic and dplyr packages
require(mosaic)
```

```{r include=FALSE}
# Some customization.  You can alter or delete as desired (if you know what you are doing).

# This changes the default colors in lattice plots.
trellis.par.set(theme=theme.mosaic())  

# knitr settings to control how R chunks work.
require(knitr)
opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small"    # slightly smaller font for code
)
# This loads the mosaic data sets.  (Could be deleted if you are not using them.)
require(mosaicData)    
require(Stat2Data)
```

This exercise corresponds to the first part of Example 1.5 on p.36 of the text.

```{r}
data(PorschePrice)
```

## Objective
We would like to assess the model previously fit to the dataset `PorschePrice`:

```{r}
lm0 <- lm(Price ~ Mileage, data=PorschePrice)
summary(lm0)
```


## Graphs
We'll start by producing the 3 graphs that will enable us to answer this question.

### A. Residual vs. Fitted Value

Produce the scatterplot of residual versus fitted values.

SOLUTION:

```{r}

```

### B. Histogram of Residuals

Produce a histogram of the residuals.

SOLUTION:

```{r}

```

### C. Normal Quantile Plot of Residuals

Produce a normal quantile plot of the residuals.

SOLUTION:

```{r}

```

## Assessment

For each of the conditions below, describe whether each is met or not met, and cite the specific plot(s) above to support your argument, if appropriate.

### 1. Linearity

SOLUTION:

### 2. Zero mean

SOLUTION:

### 3. Constant variance

SOLUTION:

### 4. Independence and Random

SOLUTION:

### 5. Normality

SOLUTION:
