---
title: "Porsche Prices with Inference"
author: ""
date: "Last Updated: Feb 12, 2015"
output: 
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---


```{r include=FALSE}
# Don't delete this chunk if you are using the mosaic package
# This loads the mosaic and dplyr packages
require(mosaic)
```

```{r include=FALSE}
# Some customization.  You can alter or delete as desired (if you know what you are doing).

# This changes the default colors in lattice plots.
trellis.par.set(theme=theme.mosaic())  

# knitr settings to control how R chunks work.
require(knitr)
opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small"    # slightly smaller font for code
)
# This loads the mosaic data sets.  (Could be deleted if you are not using them.)
require(mosaicData)    
require(Stat2Data)
```

This example is embedded throughout Chapter 2.

```{r}
data(PorschePrice)
```

## Introduction

This example was first introduced in Chapter 1 (Example 1.2 on p.27 of the text). We've already fit a simple linear regression model in the [previous exercise](../Ch01/Porsche_F.Rmd) from Chapter 1.

```{r}
m1 <- lm(Price ~ Mileage, data=PorschePrice)
summary(m1)
```

## T-test for Slope

We would like to test whether the population slope for Mileage is different from 0. 

Confirm the t-statistic calculation for slope in the model above.

SOLUTION:

```{r}
t <- -0.589/0.05665
```


Confirm the p-value calculation for slope in the model, using the `pt()` function.

SOLUTION:

```{r}
2*pt(-10.4, 28)
```


What do you conclude?

SOLUTION:

## Confidence Interval for Slope

A confidence interval for the slope of Mileage gives us a range of credible values for the population slope based on our sample.

What is a 95\% confidence interval for the slope of Mileage?

SOLUTION:

```{r}
qt(0.975, 28)
-0.589-2.05*0.05665
-0.589+2.05*0.05665
```



Interpret this confidence interval.

SOLUTION:

## ANOVA Test for Simple Linear Regression

What does the ANOVA test  tell us about the effectiveness of the model?

SOLUTION:

## R-squared

Confirm the calculation of $R^2$ using the ANOVA table.

SOLUTION:

```{r}
anova(m1)
(5565.7)/(5565.7+1439.6)
```


What is the interpretation of $R^2$ in this setting?

SOLUTION:

## Intervals for Predictions

Suppose that we are interested in a used Porsche with 50 thousand miles, namely `Mileage=50`. Produce the predicted price for this Porsche.

SOLUTION:

```{r}
pred1 <- makeFun(m1)
pred1(Mileage=50)
```


Give a 90\% confidence interval for the mean price of Porsches having 50 thousand miles.

SOLUTION:

```{r}
pred1(Mileage=50, int="confidence", level=0.9)
```


Give a 90\% prediction interval for the price of a randomly selected Porsche having 50 thousand miles.

SOLUTION:

```{r}
pred1(Mileage=50, int="prediction", level=0.9)
```


Produce a scatterplot that shows both 95\% confidence and prediction bands.

SOLUTION:

```{r}
xyplot(Price ~ Mileage, data=PorschePrice, panel=panel.lmbands)
```

